### 2016-01-15 04-evaluation.tex
Add plots + text on DKV vs qperf

>>>>

\begin{figure}[b] % [htbp]
  \centering
  \epsfig{file=plots/qperf.eps, width=0.5\textwidth}
  \caption{Performance of DKV store compared to qperf.}
  \label{fig-qperf}
\end{figure}

A thorough performance evaluation of our RDMA DKV store is outside the scope of
this paper. In figure~\ref{fig-qperf}, we provide maximum bandwidth numbers for
read operations between one server and one client for a range of payload sizes,
and compare these to the bandwidth achieved by \textit{qperf}, which shows
the best achievable preformance for Infiniband. We present \textit{qperf}
bandwidth for both RDMA read and RDMA write operations; these are nearly
identical, which corroborates the results from the Herd project for payloads
upwards from 256B. The bandwidth achieved by our DKV store mostly falls short
of the \textit{qperf} performance. For smallish packets, this is attributed
to additional per-request overhead for the DKV store. For the largest packet
size, the DKV store performance is hampered by the fact that its values
are spread over a larger memory area, whereas \textit{qperf} always reads
from the same memory locations. For packets between 8KB and 512KB, our DKV
achieves performance very close to \textit{qperf}.
